Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2024-06-07 manuscript/manuscript.Rmd
Marginal effect plot is done.

# Set general theme.
plot_theme <- ggplot2::theme_light(base_size=base_size)
plot_theme$plot.title$size <- ggplot2::rel(1.0)
plot_theme$strip.background <- ggplot2::element_blank()
plot_theme$strip.text$colour <- NULL
plot_theme$plot.margin <- grid::unit(c(2, 2, 2, 2), "points")

@@

To assess the marginal effects of process parameters, including transformation method, we first fit a regression random forest (ranger package [@Wright2017-rf] (version 0.16.0); 2000 trees, minimum node size 2, other hyperparameters default) with process parameters and task difficulty as predictors and normalised rank as response variable.

- Plot differences vs. none transformation method.
- Plot differences vs. none normalisation method and conventional transformation.

- Assess whether shift-invariant robust transformation improves machine learning results.

  - No transformation.
  - Conventional Yeo-Johnson transformation.
  - Shift sensitive Yeo-Johnson transformation.
  - Shift sensitive, robust Yeo-Johnson transformation.
  - Shift sensitive, robust Yeo-Johnson with central normality test.

  TODO: 
  - implement into familiar
  - update familiar.experiment to allow for setting external configurations (or maybe make that the default -- its definitely easier and more transparent.)

  - Add tests for out-of-bound actions (power_transform) and GOF test rejection (find_parameters).

@@

>>>>

# Set general theme.
plot_theme <- ggplot2::theme_light(base_size=base_size)
plot_theme$plot.title$size <- ggplot2::rel(0.8)
plot_theme$plot.title$hjust <- 0.5
plot_theme$strip.background <- ggplot2::element_blank()
plot_theme$strip.text$colour <- NULL
plot_theme$plot.margin <- grid::unit(c(2, 2, 2, 2), "points")

@@

To estimate the marginal effects of process parameters, including transformation method, we first fit a regression random forest (ranger package [@Wright2017-rf] (version 0.16.0); 2000 trees, minimum node size 2, other hyperparameters default) with process parameters and task difficulty as predictors and normalised rank as response variable.
The estimated marginal effects are shown in Figure \ref{fig:marginal-effect-plot}.
On the scale of normalised ranks ($[0.0, 1.0]$), the overall estimated marginal effect of using a random forest instead of generalised linear model was $0.226$.
The overall marginal effect of using z-standardisation to normalise features was $0.003$.
Transformation methods had the following marginal effects:
$0.002$ for using conventional Yeo-Johnson transformation instead of no transformation;
$-0.006$ for using robust invariant Yeo-Johnson transformation (with or without empirical central normality test) instead of no transformation; 
and $-0.008$ for using robust invariant Yeo-Johnson transformation (with or without empirical central normality test) instead of conventional Yeo-Johnson transformation.

```{r marginal-effect-plot, echo=FALSE, fig.cap=cap, fig.height=12.0, warning=FALSE}
cap <- paste0(
  "Estimated marginal effect of learners, normalisation and transformation methods on ranked model performance scores in 22800 machine learning experiments on 285 datasets. ",
  "The top-left panel shows the marginal effect of learners, i.e. random forests and generalised linear models (GLM). ",
  "Random forests outperform GLM models for all task difficulties. ",
  "The top-right panel shows the marginal effect of feature normalisation methods, i.e. no normalisation and z-standardisation. ",
  "z-standardisation is generally beneficial, but the estimated effect is neglible. ",
  "The bottom panel shows the marginal effects of different transformation methods, split by learner and normalisation method. ",
  "There is no consistent behaviour, and estimated effects are neglible. ",
  "Note that the ranges of the $x$-axes of the three main panels differ. ",
  "ECTN: empirical central normality test."
)

.plot_marginal_effects(plot_theme = plot_theme, manuscript_dir = manuscript_dir)
```

@@

We investigated the use of robust invariant power transformation for machine learning, and did not find a major positive or negative effect.
